\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

At this point it may be wise to address what we mean by prediction.
We do not attempt to predict the exact number of packets in a specific flow.
Brief reflection shows that this cannot be done accurately:
flow behavior is not deterministic---many flows exhibit the same behavior initially but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.

>>>>

At this point it may be wise to address what we mean by prediction.
Brief reflection shows that one cannot hope to accurately predict the exact behavior of flows:
flow behavior is nondeterministic---flows may exhibit the same initial behavior but subsequently behave quite differently.
The best we can do then is to predict a \emph{distribution} of possible outcomes given the observed initial behavior.
